Predicting Spotify Audio Features from Last.fm Tags

### 2023-06-02 paper/main.tex
wip

In the remainder of the article, we explain the data gathering and preparation process, as well as the data input formats and varios models.
We will explore various models for the same track and provide insights on how accurately the prediction can be, by using only Last.fm tags.

@@

% Spotify, one of the leaders in the music streaming industry...

@@

Panda and Redinho explore the use of Spotify high-level features applied to Music Emotion Recognition (MER) \cite{panda2021does}.
In particular, they identify that the energy, valence, and acousticness values, provided by the Spotify API,
are highly relevant for emotion classification.
They also achieve better performance on MER models by using their own top-100 features, and they determine that,
although these three Spotify features are relevant in terms of characterizing emotion, more features are needed for MER.

@@

Users apply these tags to
categorize music from their own perspective, which
means that tags do not fit into any structured ontology
or data model.
Tags can refer to any aspect that users consider as a valid descriptor, such as genre,
emotion, or user listenting context.

@@

The Spotify audio features are numerical values that represent high-level audio information computed from a specific
track. These values characterize a track, musically speaking,
by measuring relevant musical aspects.
For example, a danceability value of 0.95 means
that a particular song is highly suitable for dancing.

>>>>

In the remainder of the article, we explain the data gathering and preparation process, as well as the data input formats and varios models.
We will explore various models for the same track and provide insights on how accurately the prediction can be, by using only Last.fm tags.
\textcolor{red}{UNDER DEVELOPMENT}

\section{Data Sources}

Users apply these tags to
categorize music from their own perspective, which
means that tags do not fit into any structured ontology
or data model.
Tags can refer to any aspect that users consider as a valid descriptor, such as genre,
emotion, or user listening context.

Spotify, one of the leaders in the music streaming industry, provides information about each track in their catalog via the Spotify developers API.
One of the API endpoints is the audio features endpoint.

The Spotify audio features are numerical values that represent high-level audio information computed from a specific
track. These values characterize a track, musically speaking,
by measuring musical aspects that, in many of these features, are related to the perspective of the user recommendation factors.
For example, a danceability value of 0.95 means
that a particular song is highly suitable for dancing.

@@

@@

Panda and Redinho explore the use of Spotify high-level features applied to Music Emotion Recognition (MER) \cite{panda2021does}.
In particular, they identify that the energy, valence, and acousticness values, provided by the Spotify API,
are highly relevant for emotion classification.
They also achieve better performance on MER models by using their own top-100 features, and they determine that,
although these three Spotify features are relevant in terms of characterizing emotion, more features are needed for MER.
% In reality, energy is not exactly arousal, but serves as its surrogate.

@@

@@
